---
title: "Case Study"
author: "Juliet Rowe"
date: "2023-10-10"
output: github_document
---


## Load packages and  data
```{r}
library(tidyverse)
library(dplyr)
library(ggridges)
library(p8105.datasets)

data(nyc_airbnb)

str(nyc_airbnb)
```


## Brainstorm questions

- Where are airbnbs most expensive?
- How long are airbnbs active?
  - Are airbnbs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How many apts are run by one host?
  - Does that affect price?
  - Does that vary by neighborhood?
- Where are airbnbs?
  - Borough? Neighborhood?
  - Lat and long?
  

## Do some EDA
```{r}
nyc_airbnb |>
  count(neighbourhood_group)
```

```{r}
nyc_airbnb |>
  group_by(neighbourhood_group, room_type) |>
  summarize(median_price = median(price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |>
  ggplot(aes(x=price)) +
  geom_histogram() + 
  facet_grid(neighbourhood_group ~ room_type)
```

```{r}
nyc_airbnb |>
  filter(price >= 9500)
```

```{r}
nyc_airbnb |>
  filter(price < 1000, room_type == "Entire home/apt") |>
  ggplot(aes(x=price)) +
  geom_histogram() + 
  facet_grid(. ~ neighbourhood_group)
```

```{r}
nyc_airbnb |>
  filter(price < 1000, room_type == "Entire home/apt", neighbourhood_group == "Manhattan") |>
  group_by(neighbourhood) |>
  summarize(n_apt = n(), mean_price = mean(price)) |>
  arrange(desc(mean_price))
  
```

```{r}
nyc_airbnb |>
    filter(price < 1000, room_type == "Entire home/apt", neighbourhood_group == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x=price, y=neighbourhood)) + geom_density_ridges()

```




## Attempt solutions

1) How is review score impacted by location? By neighborhood, then by borough
```{r}
nyc_airbnb2 = nyc_airbnb |>
  group_by(neighbourhood) |>
  summarize(average_review_score = mean(review_scores_location, na.rm = TRUE)
  )

nyc_airbnb3 = nyc_airbnb |>
  group_by(neighbourhood_group) |>
  summarize(average_review_score = mean(review_scores_location, na.rm = TRUE)
  )
```



